Reputational Risk and Questionable Research Practices in Archaeological Science

### 2023-10-07 docs/paper.qmd
statcheck polish

```{r}
jasr_caliper <- 
  jasr_exact_zoom_plot_data %>% 
  mutate(in_caliper = ifelse(p_value %in% c(0.03875, 0.04000), 
                             "smaller", 
                             ifelse(p_value %in% c(0.04875, 0.05000), 
                                    "larger", ""))) %>% 
  filter(in_caliper != "") %>% 
  count(in_caliper)

@@

jas_caliper <- 
  jas_exact_zoom_plot_data %>% 
  mutate(in_caliper = ifelse(p_value %in% c(0.03875, 0.04000), 
                             "smaller", 
                             ifelse(p_value %in% c(0.04875, 0.05000), 
                                    "larger", ""))) %>% 
  filter(in_caliper != "") %>% 
  count(in_caliper)

@@

ggplot(jasr_exact_zoom_plot_data) +
  aes(p_value) +
  geom_histogram(bins = 27)  +
  geom_segment(x = 0.05,
            xend = 0.05,
            y = 0,
            yend = 120,
             colour = "red",
            aesthetic = 2) +
  xlim(0.03, 0.07) +
  ylim(0, 150) +
  theme_minimal() +
  ylab("frequency in JASR") +
  xlab("p-value (exactly reported in the article text)") +
  geom_richtext(
    data = jasr_df,
    aes(x, y, 
        label = label),
    fill = NA, 
    label.color = NA,
    size = 10
  ) +
  theme_light(base_size = 18)

@@

ggplot(jas_exact_zoom_plot_data) +
  aes(p_value) +
  geom_histogram(bins = 27)  +
  geom_segment(x = 0.05,
            xend = 0.05,
            y = 0,
            yend = 120,
             colour = "red",
            aesthetic = 2) +
  xlim(0.03, 0.07) +
  ylim(0, 150) +
  theme_minimal() +
  ylab("frequency in JAS") +
  xlab("p-value (exactly reported in the article text)") +
  geom_richtext(
    data = jas_df,
    aes(x, y, 
        label = label),
    fill = NA, 
    label.color = NA,
    size = 10
  ) +
  theme_light(base_size = 18)

@@

class(jasr_statcheck_results_tbl) <- c("statcheck", "data.frame")
plot(jasr_statcheck_results_tbl, APAstyle = TRUE) +
  geom_point(size = 4) +
  scale_color_viridis_d()
```

>>>>

caliper1 <- c(0.03875, 0.04000)
caliper2 <- c(0.04875, 0.05000)

jasr_caliper <- 
  jasr_exact_zoom_plot_data %>% 
  mutate(in_caliper = ifelse(p_value %in% caliper1, 
                             "smaller", 
                             ifelse(p_value %in% caliper2, 
                                    "larger", ""))) %>% 
  filter(in_caliper != "") %>% 
  count(in_caliper)

@@

jas_caliper <- 
  jas_exact_zoom_plot_data %>% 
  mutate(in_caliper = ifelse(p_value %in% caliper1, 
                             "smaller", 
                             ifelse(p_value %in% caliper2, 
                                    "larger", ""))) %>% 
  filter(in_caliper != "") %>% 
  count(in_caliper)

@@

ggplot(jasr_exact_zoom_plot_data) +
  aes(p_value) +
  geom_histogram(bins = 27)  +
  geom_segment(x = 0.05,
            xend = 0.05,
            y = 0,
            yend = 120,
             colour = "red") +
  xlim(0.03, 0.07) +
  ylim(0, 150) +
  theme_minimal() +
  ylab("frequency in JASR") +
  xlab("p-value (exactly reported in the article text)") +
  geom_richtext(
    data = jasr_df,
    aes(x, y, 
        label = label),
    fill = NA, 
    label.color = NA,
    size = 10
  ) +
  theme_light(base_size = 18)

@@

ggplot(jas_exact_zoom_plot_data) +
  aes(p_value) +
    # annotate("rect",
    #        xmin = caliper1[1],
    #        xmax = caliper1[2],
    #        ymax = 120,
    #        ymin = 0,
    #        fill = "blue",
    #        colour = "blue") +
    #   annotate("rect",
    #        xmin = caliper2[1],
    #        xmax = caliper2[2],
    #        ymax = 120,
    #        ymin = 0,
    #        fill = "blue",
    #        colour = "blue") +
  geom_histogram(bins = 27)  +
  geom_segment(x = 0.05,
            xend = 0.05,
            y = 0,
            yend = 120,
             colour = "red") +
  xlim(0.03, 0.07) +
  ylim(0, 150) +
  theme_minimal() +
  ylab("frequency in JAS") +
  xlab("p-value (exactly reported in the article text)") +
  geom_richtext(
    data = jas_df,
    aes(x, y, 
        label = label),
    fill = NA, 
    label.color = NA,
    size = 10
  ) +
  theme_light(base_size = 18)

@@

n_minor_inconsistencies <- 
  jasr_statcheck_results_tbl %>% 
  filter(error) %>% 
  nrow()

n_major_inconsistencies <- 
  jasr_statcheck_results_tbl %>% 
  filter(decision_error) %>% 
  nrow()

class(jasr_statcheck_results_tbl) <- c("statcheck", "data.frame")
plot(jasr_statcheck_results_tbl, APAstyle = TRUE) +
  geom_point(size = 5) +
  scale_color_viridis_d() +
  annotate("text",
           x = 0.3, 
           y = 0.75,
           size = 3,
           hjust = 0,
           label = paste0(nrow(jasr_statcheck_results_tbl), " papers in JASR\n",
             n_minor_inconsistencies, " with minor inconsistencies\n",
            n_major_inconsistencies, " with major inconsistencies"
                          )) +
  coord_fixed()

ggsave(here::here("figures/jasr_statcheck.png"),
       w = 8,
       h = 5,
       dpi = 600)
```
